\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/iteration3.tex
Added back implementation details for iter3
These existed earlier but were removed at some point...

\changes{After the map is created, the user can enter a quasi-mode for
  refinement by holding down on the touchpad. In this quasi-mode, one
  device lights up at a time. When the user turns their head in the
  direction of another device, the light switches to that
  device. Therefore, the user can move between devices one at a time
  with slight head movements. This prediction is implemented by
  calculating the user's direction of motion using a low-passed
  history of sensor measurements and searching through the adjacency
  map for the nearest device in that direction.}

>>>>

\changes{After the map is created, the user can enter a quasi-mode for
refinement by holding down on the touchpad. In this quasi-mode, one device
lights up at a time. When the user turns his head in the direction of another
device, the light switches to that device. Therefore, the user can move between
devices one at a time with slight head movements. This prediction is
implemented by first calculating the user's direction of motion, and searching
through the adjacency map for the nearest device in that direction.  To
calculate the direction, we maintain a circular buffer of the last 10 sensor
measurements, passed through a low pass filter. The direction is then
calculated as the difference between the last sample and the first sample.
Note that we use a hysteresis method to temporarily lock to the current device
- if the variance of the buffer is below a threshold, we assume no movement has
occurred and do not select another device.}
